Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-04-16 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Clarify the power study
Clarification before meeting

The first test statistic evaluates the behavior of the data under the null hypothesis using the empirical distribution: 
\begin{equation}
\label{Eq:test_e}
S_H= \widetilde{H}-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \widebar{Z}\right].
\end{equation}
The values should be around zero under the null hypothesis and far otherwise. 
<!-- This suggests significant differences and implies the presence of heterogeneous clutter. -->
Figure&nbsp;\ref{fig:Plot_density} shows the empirical test statistic densities for different sample sizes, and Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean, SD, variance (Var), skewness (SK), excessive kurtosis (EK) and Anderson--Darling \(p\) values for normality. 
Results with \(p\) values greater than \(0.05\) do not indicate a violation of the normality assumption. A low variance as well as a skewness and an excessive kurtosis of almost zero indicate limited dispersion, symmetry and a light tail.
Normal QQ plots confirm that there is no evidence against a normal distribution, as shown in Figure&nbsp;\ref{fig:Plot_normality_qq}.

@@

We have nominal levels of \SI{1}{\ percent}, \SI{5}{\ percent}, and
\SI{10}{\percent}. 
In terms of size, \(1000\) simulations were used for different sample sizes with satisfactory results. 
In all cases, the nominal level was achieved. 
The power generally improves with increasing sample size and number of looks.
The results are shown in Table&nbsp;\ref{tab:table_size_power}.

>>>>

The first test statistic evaluates the behavior of the data under the null hypothesis using the empirical distribution: 
<!-- ACF This is an important contribution. Highlight the rationale: under H0, \widetilde{H} (estimated) and H_{\Gamma_{\text{SAR}}}(L) (fixed) should be close. Therefore, their difference should be small. Explain why you need \widebar{Z} -->
\begin{equation}
\label{Eq:test_e}
S_H= \widetilde{H}-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \widebar{Z}\right].
\end{equation}
The values should be around zero under the null hypothesis and far otherwise. 
<!-- This suggests significant differences and implies the presence of heterogeneous clutter. -->
Figure&nbsp;\ref{fig:Plot_density} shows the empirical test statistic densities for different sample sizes, and Table&nbsp;\ref{tab:table_stat_combined} summarizes the main descriptive statistics, including mean, SD, variance (Var), skewness (SK), excessive kurtosis (EK) and Anderson--Darling \(p\) values for normality. 
Results with \(p\) values greater than \(0.05\) do not indicate a violation of the normality assumption. A low variance as well as a skewness and an excessive kurtosis of almost zero indicate limited dispersion, symmetry and a light tail.
Normal QQ plots confirm that there is no evidence against a normal distribution, as shown in Figure&nbsp;\ref{fig:Plot_normality_qq}.

@@

We have nominal levels of \SI{1}{\ percent}, \SI{5}{\ percent}, and
\SI{10}{\percent}. 
In terms of size, \(1000\) simulations were used for different sample sizes with satisfactory results. 
In all cases, the nominal level was achieved. 
The power generally improves with increasing sample size and number of looks.
The results are shown in Table&nbsp;\ref{tab:table_size_power}.
<!-- ACF Please clarify which alternatives you used for the power -->
